\bf Estimating the number of clusters using cross-validation

### 2018-03-01 cvclust.tex
AE point 2

>>>>

For the competing methods, some might take issue with the fact that we are
using default parameter settings.  In many other benchmark comparisons, one
would choose the tuning parameters using some form of cross-validation. In our
case, this is not an option. We are in an \emph{unsupervised} setting, so
there is no clear way to set the tuning parameters. We must rely on the
defaults from the implementations of these methods.
